---
title: "zomator"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{zomato}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Intro to the zomator package
A package that using API to access to [Zomato](https://developers.zomato.com/).

## Installation

```{r}
install.packages("devtools")
devtools::install_github("yitang310/zomator")
```

Then load the package into the R sesssion.

## Usage

Inside `zomator`, there are 12 functions:

| Category |  Function Name  | Description  | Parameters | Example |
|  ----  | ----  | ---- | ---- | ---- |
| Common | get_categories | Get list of Categories | *key* | get_categories('key') |
| | get_cities  | Get city details | *key, q, lat, lon, city_ids, count* | get_cities('key', q='van') |
| | get_collections | Get Zomato collections in a city | *key, city_id, lat, lon, count* | get_collections('key', city_id=256) |
| | get_cuisines | Get list of all cuisines in a city | *key, city_id, lat, lon* | get_cuisines('key', city_id=256)
| | get_establishments | Get list of restaurant types in a city | *key, city_id, lat, lon* | get_establishments(key, city_id = 280) |
| | get_geocode | Get location details based on coordinates | *key, lat, lon* | get_geocode(key, 1.2, 2.3) |
| Location | get_location_details | Get Zomato location details | *key, entity_id, entity_type* | get_location_details(key, 1, "city") |
| | get_locations | Search for locations | *key, query, lat, lon, count* | get_locations(key, "van") |
| Restaurant | get_dailymenu | Get daily menu of a restaurant |  *key, res_id* | get_restaurant('key', res_id="16774318") |
| | get_restaurant | Get restaurant details | *key, res_id* | get_restaurant('key', res_id="16774318") |
| | get_reviews | Get restaurant reviews | *key, res_id* | get_reviews('key', res_id="16774318") |
| | get_search | Search for restaurants | *key, q, entity_id, entity_type, start, count, lat, lon, radius, cuisines, establishment_type, collection_id, category, sort, order* | get_search('key', q="van") |

## Work Distribution

**Readme:** Yang (editor)

**Description:** Tang (editor)

**Vignettes:** Yang (main editor), Tang (editor), Li (editor)


**R functions:**

- get_categories: Tang (author)

- get_cities: Tang (author)

- get_collections: Tang (author)

- get_cuisines: Tang (author)

- get_establishments: Li (author), Tang (editor)

- get_geocode: Li (author), Tang (editor)

- get_location_details: Li (author), Yang (editor)

- get_locations: Li (author), Tang (editor)

- get_dailymenu: Yang (author) 

- get_restaurant: Yang (author)

- get_reviews: Yang (author)

- get_search: Yang (author)


**Tests:**

testpart1: Tang (author)

testpart2: Li (author)

testpart3: Yang (author)


```{r setup}
library(zomator)
```

* requirement  
 go to [Zomato Web Site](https://developers.zomato.com/api#headline1) request An API Key

# please replace "key" with your API key 

```{r}
get_categories(key=key)
```

```
   categories.id          categories.name
1              1                 Delivery
2              2                 Dine-out
3              3                Nightlife
4              4              Catching-up
5              5                 Takeaway
6              6                    Cafes
7              7              Daily Menus
8              8                Breakfast
9              9                    Lunch
10            10                   Dinner
11            11              Pubs & Bars
12            13 Pocket Friendly Delivery
13            14          Clubs & Lounges

```

```{r}
get_cities(key=key,q="van")
```

```
      id                name country_id  country_name
1   9560     Van Alstyne, TX        216 United States
2   6133       Van Buren, ME        216 United States
3   6702       Van Buren, MO        216 United States
4   7744       Van Etten, NY        216 United States
5   9126        Van Horn, TX        216 United States
6   9618       Van Vleck, TX        216 United States
7    256 Metro Vancouver, BC         37        Canada
8  10650       Vancouver, WA        216 United States
9   5849       Vanceburg, KY        216 United States
10  5051        Vandalia, IL        216 United States

                                              country_flag_url should_experiment_with
1  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
2  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
3  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
4  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
5  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
6  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
7   https://b.zmtcdn.com/images/countries/flags/country_37.png                      0
8  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
9  https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
10 https://b.zmtcdn.com/images/countries/flags/country_216.png                      0
   
   has_go_out_tab discovery_enabled has_new_ad_format is_state state_id
1               0                 0                 0        0      111
2               0                 0                 0        0       89
3               0                 0                 0        0       92
4               0                 0                 0        0      103
5               0                 0                 0        0      111
6               0                 0                 0        0      111
7               0                 0                 0        0      121
8               0                 0                 0        0      115
9               0                 0                 0        0       85
10              0                 0                 0        0       82
         
         state_name state_code
1             Texas         TX
2             Maine         ME
3          Missouri         MO
4    New York State         NY
5             Texas         TX
6             Texas         TX
7  British Columbia         BC
8  Washington State         WA
9          Kentucky         KY
10         Illinois         IL

```

```{r}
get_collections(key=key,city_id=256)
```

```
   collection.collection_id collection.res_count
1                         1                   30
2                       760                   28
3                         5                   27
4                         6                   15
5                         8                   16
6                        65                   22
7                        40                   28
8                       125                   23
9                        48                   15
10                       39                   18
11                       14                   22
12                       35                   14
13                       46                   22
14                       24                   13
15                       41                   21
16                      203                   20
17                      112                   18
18                      207                   28
19                       33                   29
20                      204                   19
21                      222                   25
22                       15                   25
23                      201                   17
24                       64                   14
25                      429                   20
26                      446                   18
27                      714                   18
28                      237                   16
29                      318                   14
30                      447                   32
31                      235                   25
 
                                                                      collection.image_url
1    https://b.zmtcdn.com/data/collections/b53772a204429cb9b42313d6dc22bf3c_1556018415.jpg
2    https://b.zmtcdn.com/data/collections/0297238e2a8c0fcd5e75e0b7baa7093d_1455565224.jpg
3    https://b.zmtcdn.com/data/collections/d38669ed7b829ceb2814678420a629da_1560353561.jpg
4    https://b.zmtcdn.com/data/collections/33ebdc279ce63a293c52095b1facf611_1539323119.jpg
5  https://b.zmtcdn.com/data/collections/52d2ea4a19bee4d876e42d14574b2508_1427378290_l.jpg
6    https://b.zmtcdn.com/data/collections/73391cc46aa0d33d5c5cf3bd09981bc6_1469073198.jpg
7    https://b.zmtcdn.com/data/collections/bc0c37f8fc87da896641714b9ef7f0b7_1575621158.jpg
8    https://b.zmtcdn.com/data/collections/b386fe9dca9543d888e43fb8d3425436_1477292962.jpg
9  https://b.zmtcdn.com/data/collections/3348431bcaa616e6cd3ccadc95ceca63_1427263670_l.jpg
10   https://b.zmtcdn.com/data/collections/8ba9c4eefe77e89afabda22482f13031_1460092296.jpg
11   https://b.zmtcdn.com/data/collections/0fecfe2b205a9dd7da273f6841115eef_1454036759.jpg
12 https://b.zmtcdn.com/data/collections/b5a5caace052be929d9829d32ae1c591_1441697242_l.jpg
13 https://b.zmtcdn.com/data/collections/1074db54a4fe3de129f7f595e62cf89d_1418393267_l.jpg
14 https://b.zmtcdn.com/data/collections/fb1a0edf9843e7a9145d44d0edaf553a_1421673616_l.jpg
15 https://b.zmtcdn.com/data/collections/d0a0e32df636a9dfbf850f13a38aa834_1446629668_l.jpg
16 https://b.zmtcdn.com/data/collections/ead72be0dfd00a6577b9a668bf5c393b_1429785802_l.jpg
17 https://b.zmtcdn.com/data/collections/d54df30563212e846bf79dd1ba0f1de4_1419918252_l.jpg
18 https://b.zmtcdn.com/data/collections/07462839e697e1e78c28dd4013d323a6_1442300754_l.jpg
19 https://b.zmtcdn.com/data/collections/30f9382a8d53b25e258fd0564523a7b6_1418398601_l.jpg
20 https://b.zmtcdn.com/data/collections/e646f44bd5e27764586a4bec6add3b75_1430816900_l.jpg
21 https://b.zmtcdn.com/data/collections/068705072f757d7aad443e55085dc61f_1430118583_l.jpg
22 https://b.zmtcdn.com/data/collections/10dcdac2c6d08f9bae81b04042c34544_1438664251_l.jpg
23 https://b.zmtcdn.com/data/collections/c5e0ef119285ca2236a884b32b9d4f18_1445595921_l.jpg
24 https://b.zmtcdn.com/data/collections/5b0cc8f2aae006cf0635c990b4a1a110_1421849036_l.jpg
25 https://b.zmtcdn.com/data/collections/52ddbf4038db984190ddb910311225e9_1426837329_l.jpg
26 https://b.zmtcdn.com/data/collections/0707137915a22b40b4d5e8274f47d791_1427179044_l.jpg
27 https://b.zmtcdn.com/data/collections/40d01ac6a776346c8fd7b66c8564a3ec_1442312930_l.jpg
28 https://b.zmtcdn.com/data/collections/58ada2fe8114c2e8e84e5eba4eaa36ed_1428383289_l.jpg
29 https://b.zmtcdn.com/data/collections/979cdb510dd79262b6b7391708b64550_1444636538_l.jpg
30 https://b.zmtcdn.com/data/collections/f2eab8b5e872abce579d51d3b50d294d_1427180187_l.jpg
31 https://b.zmtcdn.com/data/collections/8376ac139adff6fba677dfab9015e097_1427532216_l.jpg
           
                                                                                                             collection.url
1            https://www.zomato.com/penticton-bc/top-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
2                  https://www.zomato.com/penticton-bc/mealshare?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
3                https://www.zomato.com/penticton-bc/best-burger?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
4     https://www.zomato.com/penticton-bc/late-night-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
5         https://www.zomato.com/penticton-bc/hidden-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
6                      https://www.zomato.com/penticton-bc/sushi?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
7             https://www.zomato.com/penticton-bc/dessert-places?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
8             https://www.zomato.com/penticton-bc/weekend-brunch?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
9                    https://www.zomato.com/penticton-bc/seafood?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
10       https://www.zomato.com/penticton-bc/healthy-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
11      https://www.zomato.com/penticton-bc/sea-view-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
12         https://www.zomato.com/penticton-bc/ramen-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
13          https://www.zomato.com/penticton-bc/date-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
14       https://www.zomato.com/penticton-bc/unusual-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
15                https://www.zomato.com/penticton-bc/craft-beer?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
16 https://www.zomato.com/penticton-bc/great-chinese-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
17          https://www.zomato.com/penticton-bc/best-pizza-spots?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
18                  https://www.zomato.com/penticton-bc/best-pho?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
19           https://www.zomato.com/penticton-bc/artisanal-cafes?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
20                https://www.zomato.com/penticton-bc/best-tacos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
21           https://www.zomato.com/penticton-bc/best-sandwiches?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
22                https://www.zomato.com/penticton-bc/sports-bar?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
23          https://www.zomato.com/penticton-bc/thai-restaurants?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
24                  https://www.zomato.com/penticton-bc/high-tea?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
25             https://www.zomato.com/penticton-bc/farm-to-table?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
26                 https://www.zomato.com/penticton-bc/breweries?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
27              https://www.zomato.com/penticton-bc/winter-cafes?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
28              https://www.zomato.com/penticton-bc/best-poutine?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
29              https://www.zomato.com/penticton-bc/heated-patio?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
30                https://www.zomato.com/penticton-bc/work-cafes?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
31       https://www.zomato.com/penticton-bc/best-hangover-cures?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
          
          collection.title
1       Trending This Week
2                Mealshare
3          Kickass Burgers
4   Late Night Restaurants
5              Hidden Gems
6              Super Sushi
7              Sweet Tooth
8         Weekend Brunches
9            Super Seafood
10          Healthy Eating
11                Sea View
12                   Ramen
13              Date Night
14           Unique Dining
15              Craft Beer
16           Great Chinese
17             Upper Crust
18 Restaurants Serving Pho
19         Artisanal cafes
20             Tasty Tacos
21        Super Sandwiches
22             Sports Bars
23           Terrific Thai
24                High Tea
25           Farm-to-table
26        Badass breweries
27              Cozy Cafés
28         Perfect Poutine
29            Heated patio
30             Work spaces
31           Greasy Spoons
                                                                                                 
                                                                                                 collection.description
1                                                                            Most popular restaurants in town this week
2                                                                      Feed someone in need the next time you dine out.
3                                                                                  Chow down on a cheeselicious burger!
4  Banish those midnight cravings with our handy list of late night restaurants serving all your favourite comfort food
5                                                                    The definitive list of hidden gems you need to try
6              Classic maki-style rolls, sashimi or nigiri sushi, hit up these spots for your favourite Japanese snack 
7       From cookies and doughnuts to ice cream and cakes, knock yourself out with these classic and creative desserts 
8                                   Sit back, enjoy a wide spread and forget that a new work week is sneaking up on you
9                                                                                       The best seafood places in town
10                                                                                             Grub that's good for you
11                                                                 Amazing food, amazing views. How's that for win-win?
12                                                                                     The city's best ramen, and more!
13                                                                              Ideal spots to enjoy a romantic evening
14                                                                           Dining experiences you'll remember forever
15                                                                                         The best house brews in town
16                                                            Some of the best Chinese food that your city has to offer
17                                                                             For the delicious, cheesy mess you love.
18                                  Hit up these places for some of the best soul warming Vietnamese noodle soup - Pho!
19                                                                              One handcrafted magic in a cup, please.
20                                                                      Eat your way through the best taquerias in town
21                                                   Two slices of bread, meat and veggies and the rest is mere details
22                                                                   The best places to enjoy some sport with your meal
23                                                           The leading pad thai, rice noodles & peanut sauces in town
24                                                                                              Fancy an evening cuppa?
25                                        Organic, healthy and all natural food, from the fields straight to your plate
26                                                                          Sometimes, bottled beer just doesn't cut it
27                                             Here is our list of warm and cosy places to curl up with a cup of coffee
28                                                               Fries, cheese and gravy. What could possibly go wrong?
29                                                        Keep warm while you drink up at the city's best heated patios
30                                                                      Get a bit to eat to go with the peace and quiet
31                                                                                 These places will sort you right out
           
           collection.share_url
1    http://www.zoma.to/c-256/1
2  http://www.zoma.to/c-256/760
3    http://www.zoma.to/c-256/5
4    http://www.zoma.to/c-256/6
5    http://www.zoma.to/c-256/8
6   http://www.zoma.to/c-256/65
7   http://www.zoma.to/c-256/40
8  http://www.zoma.to/c-256/125
9   http://www.zoma.to/c-256/48
10  http://www.zoma.to/c-256/39
11  http://www.zoma.to/c-256/14
12  http://www.zoma.to/c-256/35
13  http://www.zoma.to/c-256/46
14  http://www.zoma.to/c-256/24
15  http://www.zoma.to/c-256/41
16 http://www.zoma.to/c-256/203
17 http://www.zoma.to/c-256/112
18 http://www.zoma.to/c-256/207
19  http://www.zoma.to/c-256/33
20 http://www.zoma.to/c-256/204
21 http://www.zoma.to/c-256/222
22  http://www.zoma.to/c-256/15
23 http://www.zoma.to/c-256/201
24  http://www.zoma.to/c-256/64
25 http://www.zoma.to/c-256/429
26 http://www.zoma.to/c-256/446
27 http://www.zoma.to/c-256/714
28 http://www.zoma.to/c-256/237
29 http://www.zoma.to/c-256/318
30 http://www.zoma.to/c-256/447
31 http://www.zoma.to/c-256/235

```

```{r}
get_cuisines(key=key,city_id=256)
```

```
    cuisine.cuisine_id cuisine.cuisine_name
1                 1035               Afghan
2                  152              African
3                    1             American
4                    4              Arabian
5                    3                Asian
6                  401         Asian Fusion
7                  131           Australian
8                  201             Austrian
9                  193                  BBQ
10                 955               Bagels
11                   5               Bakery
12                 227             Bar Food
13                 132              Belgian
14                 270            Beverages
15                 159            Brazilian
16                 182            Breakfast
17                 133              British
18                 247           Bubble Tea
19                 168               Burger
20                  22              Burmese
21                  30                 Cafe
22                 491                Cajun
23                 111            Cambodian
24                 381             Canadian
25                 121            Cantonese
26                 158            Caribbean
27                  25              Chinese
28                 161       Coffee and Tea
29                 287            Colombian
30                 144         Contemporary
31                  35          Continental
32                 153                Cuban
33                 192                 Deli
34                 100             Desserts
35                 411              Dim Sum
36                 541                Diner
37                 959               Donuts
38                 268          Drinks Only
39                 651     Eastern European
40                 149            Ethiopian
41                  38             European
42                  40            Fast Food
43                 112             Filipino
44                 271          Finger Food
45                 298       Fish and Chips
46                  45               French
47                 501        Frozen Yogurt
48                 274               Fusion
49                 134               German
50                 156                Greek
51                 181                Grill
52                 441        Hakka Chinese
53                 521             Hawaiian
54                 143         Healthy Food
55                 791      Hong Kong Style
56                 228            Hungarian
57                 233            Ice Cream
58                 148               Indian
59                 114           Indonesian
60                 154        International
61                 140              Iranian
62                 135                Irish
63                  55              Italian
64                 207             Jamaican
65                  60             Japanese
66                 265               Jewish
67                 164               Juices
68                 178                Kebab
69                  67               Korean
70                 136       Latin American
71                  66             Lebanese
72                  69            Malaysian
73                  70        Mediterranean
74                  73              Mexican
75                 137       Middle Eastern
76                  74            Mongolian
77                 147             Moroccan
78                 117             Nepalese
79                  50         North Indian
80                 861     Northern Chinese
81                 963    Pacific Northwest
82                 139            Pakistani
83                 209            Pan Asian
84                 183           Patisserie
85                  81              Persian
86                 162             Peruvian
87                  82                Pizza
88                 219               Polish
89                  87           Portuguese
90                 983             Pub Food
91                 511            Quebecois
92                 320                Ramen
93                  27            Raw Meats
94                  84              Russian
95                 998                Salad
96                 601          Salvadorean
97                 304             Sandwich
98                  83              Seafood
99                 831             Shanghai
100                128              Sichuan
101                119          Singaporean
102                461            Soul Food
103                 85         South Indian
104                471             Southern
105                 89              Spanish
106                 86           Sri Lankan
107                141                Steak
108                 90          Street Food
109                177                Sushi
110                211              Swedish
111                213                Swiss
112                212               Syrian
113                190            Taiwanese
114                179                Tapas
115                163                  Tea
116                150              Tex-Mex
117                 95                 Thai
118                 93              Tibetan
119                631         Trinbagonian
120                142              Turkish
121                451            Ukrainian
122                308           Vegetarian
123                641           Venezuelan
124                 99           Vietnamese
125                851             Xinjiang
```

```{r}
get_establishments(key =key,city_id = 256)
```

```
   establishment.id establishment.name
1                16      Casual Dining
2                21        Quick Bites
3                 1               Café
4                 7                Bar
5                23    Dessert Parlour
6                31             Bakery
7               278           Wine Bar
8               295        Noodle Shop
9                41      Beverage Shop
10               18        Fine Dining
11              285        Fast Casual
12                5             Lounge
13               20         Food Court
14              294            Izakaya
15                6                Pub
16                8               Club
17               81         Food Truck
18              281          Fast Food
19              284          Juice Bar
20              271      Sandwich Shop
21              161       Microbrewery
22              275           Pizzeria
23              272       Cocktail Bar
24              286        Coffee Shop
25              261     Ice Cream Shop
26              309         Steakhouse
27              283            Brewery
28               91             Bistro
29              141         Patisserie
30              290           Vineyard

```
```{r}
get_geocode(key=key,1.2,2.3)
```

```{r}
data_geocode <- get_geocode(key=key,1.2,2.3)
plot(data_geocode$restaurant.location.latitude,data_geocode$restaurant.location.longitude,main="The Locations of 10 Restaurants in Alamo Heights San Antonio")
```
```
                 restaurant.apikey restaurant.id               restaurant.name
2 00b8630a1745b3dda0d7ec926bba5c04      17153325                Florio's Pizza
3 00b8630a1745b3dda0d7ec926bba5c04      17154519                        Soluna
4 00b8630a1745b3dda0d7ec926bba5c04      17157816                   Stone Werks
5 00b8630a1745b3dda0d7ec926bba5c04      17154889  Twin Sisters Bakery and Cafe
6 00b8630a1745b3dda0d7ec926bba5c04      17154602 Sushi Zushi - Lincoln Heights
7 00b8630a1745b3dda0d7ec926bba5c04      17160338                Torchy's Tacos
8 00b8630a1745b3dda0d7ec926bba5c04      17153353                   Frederick's
9 00b8630a1745b3dda0d7ec926bba5c04      17154147                       Orderup
                                                                                                                            restaurant.url
2                https://www.zomato.com/san-antonio/florios-pizza-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
3                       https://www.zomato.com/san-antonio/soluna-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
4                  https://www.zomato.com/san-antonio/stone-werks-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
5 https://www.zomato.com/san-antonio/twin-sisters-bakery-and-cafe-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
6  https://www.zomato.com/san-antonio/sushi-zushi-lincoln-heights-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
7                https://www.zomato.com/san-antonio/torchys-tacos-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
8                   https://www.zomato.com/san-antonio/fredericks-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
9                      https://www.zomato.com/san-antonio/orderup-alamo-heights?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
 
  restaurant.switch_to_order_menu              restaurant.cuisines
2                               0                   Pizza, Italian
3                               0                          Mexican
4                               0 Burger, Sandwich, Seafood, Pizza
5                               0                             Cafe
6                               0                            Sushi
7                               0           Taco, Tex-Mex, Mexican
8                               0                    Asian, French
9                               0         Mexican, American, Pizza
  
  restaurant.average_cost_for_two restaurant.price_range restaurant.currency
2                              10                      1                   $
3                              35                      3                   $
4                              25                      2                   $
5                              10                      1                   $
6                              25                      2                   $
7                              10                      1                   $
8                              40                      3                   $
9                              10                      1                   $
  
  restaurant.offers restaurant.opentable_support restaurant.is_zomato_book_res
2              NULL                            0                             0
3              NULL                            0                             0
4              NULL                            0                             0
5              NULL                            0                             0
6              NULL                            0                             0
7              NULL                            0                             0
8              NULL                            0                             0
9              NULL                            0                             0
  
  restaurant.mezzo_provider restaurant.is_book_form_web_view
2                     OTHER                                0
3                     OTHER                                0
4                     OTHER                                0
5                     OTHER                                0
6                     OTHER                                0
7                     OTHER                                0
8                     OTHER                                0
9                     OTHER                                0
  
  restaurant.book_form_web_view_url restaurant.book_again_url
2                                                            
3                                                            
4                                                            
5                                                            
6                                                            
7                                                            
8                                                            
9                                                            
                                                                                                                                                                                                                                                                                                            restaurant.thumb
2                                                                                                                                                 
3 https://b.zmtcdn.com/data/res_imagery/17154519_RESTAURANT_f4b0fa1968829461fb2959aef4e8278b_c.jpg?fit=around%7C200%3A200&crop=200%3A200%3B%2A%2C%2A
4                                                                                                                                                 
5                                                                                                                                                 
6      https://b.zmtcdn.com/data/res_imagery/17154600_CHAIN_6e908c64b8fa11ae884bd915d5778d10_c.jpg?fit=around%7C200%3A200&crop=200%3A200%3B%2A%2C%2A
7                                                                                                                                                  
8                                                                                                                                                 
9                                                                                                                                                   
      
                                                                                                                                   restaurant.photos_url
2                https://www.zomato.com/san-antonio/florios-pizza-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
3                       https://www.zomato.com/san-antonio/soluna-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
4                  https://www.zomato.com/san-antonio/stone-werks-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
5 https://www.zomato.com/san-antonio/twin-sisters-bakery-and-cafe-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
6  https://www.zomato.com/san-antonio/sushi-zushi-lincoln-heights-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
7                https://www.zomato.com/san-antonio/torchys-tacos-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
8                   https://www.zomato.com/san-antonio/fredericks-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
9                      https://www.zomato.com/san-antonio/orderup-alamo-heights/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
                                                                                                                                                                                      
                                                                                                                                                                                                                                                                                                                            restaurant.menu_url
2 https://www.zomato.com/san-antonio/florios-pizza-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
3        https://www.zomato.com/san-antonio/soluna-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
4   https://www.zomato.com/san-antonio/stone-werks-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
5 https://www.zomato.com/san-antonio/twin-sisters-bakery-and-cafe-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
6 https://www.zomato.com/san-antonio/sushi-zushi-lincoln-heights-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
7 https://www.zomato.com/san-antonio/torchys-tacos-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
8    https://www.zomato.com/san-antonio/fredericks-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
9       https://www.zomato.com/san-antonio/orderup-alamo-heights/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
                                                                         
                                                                         restaurant.featured_image
2                                                                                                 
3 https://b.zmtcdn.com/data/res_imagery/17154519_RESTAURANT_f4b0fa1968829461fb2959aef4e8278b_c.jpg
4                                                                                                 
5                                                                                                 
6      https://b.zmtcdn.com/data/res_imagery/17154600_CHAIN_6e908c64b8fa11ae884bd915d5778d10_c.jpg
7                                                                                                 
8                                                                                                 
9                                                                                                 
 
  restaurant.has_online_delivery restaurant.is_delivering_now
2                              0                            0
3                              0                            0
4                              0                            0
5                              0                            0
6                              0                            0
7                              0                            0
8                              0                            0
9                              0                            0
 
  restaurant.include_bogo_offers          restaurant.deeplink
2                           TRUE zomato://restaurant/17153325
3                           TRUE zomato://restaurant/17154519
4                           TRUE zomato://restaurant/17157816
5                           TRUE zomato://restaurant/17154889
6                           TRUE zomato://restaurant/17154602
7                           TRUE zomato://restaurant/17160338
8                           TRUE zomato://restaurant/17153353
9                           TRUE zomato://restaurant/17154147
 
  restaurant.is_table_reservation_supported restaurant.has_table_booking
2                                         0                            0
3                                         0                            0
4                                         0                            0
5                                         0                            0
6                                         0                            0
7                                         0                            0
8                                         0                            0
9                                         0                            0
     
                                                                                                                                   restaurant.events_url
2                https://www.zomato.com/san-antonio/florios-pizza-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
3                       https://www.zomato.com/san-antonio/soluna-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
4                  https://www.zomato.com/san-antonio/stone-werks-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
5 https://www.zomato.com/san-antonio/twin-sisters-bakery-and-cafe-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
6  https://www.zomato.com/san-antonio/sushi-zushi-lincoln-heights-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
7                https://www.zomato.com/san-antonio/torchys-tacos-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
8                   https://www.zomato.com/san-antonio/fredericks-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
9                      https://www.zomato.com/san-antonio/orderup-alamo-heights/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
  
  restaurant.R.res_id restaurant.R.has_menu_status.delivery
2            17153325                                    -1
3            17154519                                    -1
4            17157816                                    -1
5            17154889                                    -1
6            17154602                                    -1
7            17160338                                    -1
8            17153353                                    -1
9            17154147                                    -1
  
  restaurant.R.has_menu_status.takeaway
2                                    -1
3                                    -1
4                                    -1
5                                    -1
6                                    -1
7                                    -1
8                                    -1
9                                    -1
                               
                                       restaurant.location.address
2           7701 Broadway Street, Alamo Heights, San Antonio 78209
3                          7959 Broadway Street, San Antonio 78209
4                999 East Basse Road, Suite 130, San Antonio 78209
5                   6322 N New Braunfels Avenue, San Antonio 78209
6                                999 East Basse Road Ste 186 78209
7                                  999 East. Basse Road #183 78209
8 7701 Broadway Street, Suite 20, Alamo Heights, San Antonio 78209
9                              999 E Basse Road, San Antonio 78209
  
  restaurant.location.locality restaurant.location.city restaurant.location.city_id
2                Alamo Heights              San Antonio                         304
3                Alamo Heights              San Antonio                         304
4                Alamo Heights              San Antonio                         304
5                Alamo Heights              San Antonio                         304
6                Alamo Heights              San Antonio                         304
7                Alamo Heights              San Antonio                         304
8                Alamo Heights              San Antonio                         304
9                Alamo Heights              San Antonio                         304
  
  restaurant.location.latitude restaurant.location.longitude
2                29.4996450000                -98.4666940000
3                29.5065170000                -98.4663740000
4                29.4971661000                -98.4664773000
5                29.4881140000                -98.4591260000
6                29.4969200000                -98.4697400000
7                29.4975892000                -98.4705400000
8                29.4996450000                -98.4666940000
9                29.4967380000                -98.4682220000
  
  restaurant.location.zipcode restaurant.location.country_id
2                       78209                            216
3                       78209                            216
4                       78209                            216
5                       78209                            216
6                       78209                            216
7                       78209                            216
8                       78209                            216
9                       78209                            216
 
  restaurant.location.locality_verbose restaurant.user_rating.aggregate_rating
2           Alamo Heights, San Antonio                                     4.8
3           Alamo Heights, San Antonio                                     4.0
4           Alamo Heights, San Antonio                                     3.7
5           Alamo Heights, San Antonio                                     4.0
6           Alamo Heights, San Antonio                                     3.9
7           Alamo Heights, San Antonio                                     3.8
8           Alamo Heights, San Antonio                                     3.9
9           Alamo Heights, San Antonio                                     4.0
  
  restaurant.user_rating.rating_text restaurant.user_rating.rating_color
2                          Excellent                              3F7E00
3                          Very Good                              5BA829
4                               Good                              9ACD32
5                          Very Good                              5BA829
6                               Good                              9ACD32
7                               Good                              9ACD32
8                               Good                              9ACD32
9                          Very Good                              5BA829
  
  restaurant.user_rating.votes restaurant.user_rating.rating_obj.title.text
2                          417                                          4.8
3                          141                                          4.0
4                          148                                          3.7
5                          178                                          4.0
6                          139                                          3.9
7                           70                                          3.8
8                           78                                          3.9
9                          107                                          4.0
  
  restaurant.user_rating.rating_obj.bg_color.type
2                                            lime
3                                            lime
4                                            lime
5                                            lime
6                                            lime
7                                            lime
8                                            lime
9                                            lime
  
  restaurant.user_rating.rating_obj.bg_color.tint
2                                             800
3                                             600
4                                             600
5                                             600
6                                             600
7                                             600
8                                             600
9                                             600

```

```{r}
get_location_details(key=key,1,"city")
```

```{r}
data_location_details<-get_location_details(key=key,256,"city")
barplot(data_location_details$all_reviews_count,names.arg=data_location_details$name,las=2,cex.names = 0.5,cex.lab = 0.65, main = "Reviews Count for 10 Restaurants in Metro Vancouver British Columbia",cex.main=0.9)
barplot(data_location_details$photo_count,names.arg=data_location_details$name,las=2,cex.names = 0.5,cex.lab = 0.65, main = "Photo Count of 10 Restaurants in Metro Vancouver British Columbia",cex.main=0.9)
```
```
         id                 name switch_to_order_menu
1  19012596         One8 Commune                    0
2  19214877            FlyDining                    0
3  18562836               Diggin                    0
4      2742 Bukhara - ITC Maurya                    0
5    301489      Barbeque Nation                    0
6      2298           Haldiram's                    0
7      5004   Om Sweets & Snacks                    0
8    310078          Burger King                    0
9    303371      Barbeque Nation                    0
10     2004        Indian Accent                    0
                                                 
                                                                      cuisines
1                               Finger Food, Continental, Mediterranean, Asian
2                                                  Continental, Asian, Italian
3                                                     Cafe, Italian, Beverages
4                                                          North Indian, Kebab
5                                                   North Indian, Chinese, BBQ
6  Mithai, North Indian, Street Food, South Indian, Bakery, Chinese, Fast Food
7                       Mithai, North Indian, Fast Food, South Indian, Chinese
8                                                             Burger, American
9                                                   North Indian, Chinese, BBQ
10                                                               Modern Indian
                                  
                                   timings average_cost_for_two price_range currency
1                     11 AM to 12 Midnight                 2500           4      Rs.
2                  4pm – 11:30pm (Mon-Sun)                 5000           4      Rs.
3                 11:30am – 10pm (Mon-Sun)                 1300           3      Rs.
4       12:30 PM to 3 PM, 7 PM to 11:45 PM                 6500           4      Rs.
5  12 Noon to 3:30 PM, 6:30 PM to 11:30 PM                 1600           3      Rs.
6                  8:30am – 11pm (Mon-Sun)                  600           2      Rs.
7                  8am – 10:30pm (Mon-Sun)                  500           2      Rs.
8                           10 AM to 11 PM                  500           2      Rs.
9  12 Noon to 3:30 PM, 6:30 PM to 11:30 PM                 1600           3      Rs.
10    12 Noon to 2:30 PM, 7 PM to 10:30 PM                 5000           4      Rs.
                                                                                                                                                                                                                                                                                                                                    highlights
1 Dinner, Cash, Credit Card, Lunch, Takeaway Available, Debit Card, Valet Parking Available, Indoor Seating, Table booking recommended, Sneakpeek, Fullbar, Free Wifi, Air Conditioned
2 Dinner, Cash, Debit Card, Lunch, Credit Card, Outdoor Seating, Table booking recommended
3 Lunch, Takeaway Available, Debit Card, Dinner, Cash, Credit Card, Outdoor Seating, Air Conditioned, Indoor Seating
4 Dinner, Credit Card, Lunch, Cash, Debit Card, Valet Parking Available, Indoor Seating, Table booking recommended, Air Conditioned, Luxury Dining, Fullbar, 4/5 Star, Restricted Entry, Wheelchair Accessible
5 Dinner, Credit Card, Debit Card, Lunch, Cash, Buffet, Fullbar, Indoor Seating, Air Conditioned, Wifi, Outdoor Seating, Table booking recommended
6 Dinner, Delivery, Credit Card, Debit Card, Lunch, Cash, Takeaway Available, Breakfast, Indoor Seating, Air Conditioned, Digital Payments Accepted, Desserts and Bakes
7 Cash, Takeaway Available, Credit Card, Debit Card, Dinner, Delivery, Breakfast, Lunch, Indoor Seating, Air Conditioned, Pure Veg, Desserts and Bakes
8 Mall Parking, Takeaway Available, Debit Card, Dinner, Cash, Delivery, Credit Card, Lunch, Air Conditioned, Wheelchair Accessible, Indoor Seating, Ticket Restaurant, Axis Bank - Dining Delights
9 Dinner, Credit Card, Debit Card, Lunch, Cash, Indoor Seating, Air Conditioned, Table booking recommended, Buffet
10 Lunch, Cash, Debit Card, Dinner, Credit Card, Table booking recommended, Fullbar, 4/5 Star, Wifi, Valet Parking Available, Indoor Seating, Air Conditioned, Luxury Dining

   offers opentable_support is_zomato_book_res mezzo_provider is_book_form_web_view
1    NULL                 0                  0          OTHER                     0
2    NULL                 0                  0          OTHER                     0
3    NULL                 0                  0          OTHER                     0
4    NULL                 0                  0          OTHER                     0
5    NULL                 0                  0          OTHER                     0
6    NULL                 0                  0          OTHER                     0
7    NULL                 0                  0          OTHER                     0
8    NULL                 0                  0          OTHER                     0
9    NULL                 0                  0          OTHER                     0
10   NULL                 0                  0          OTHER                     0
   
   all_reviews_count photo_count
1                366         450
2                 21          37
3               1670        4515
4               1833        1479
5               2248        3358
6               1254        1953
7               1192         529
8               1685        1789
9               1570        2093
10              1532        5645

   medio_provider has_online_delivery is_delivering_now include_bogo_offers
1               1                   0                 0                TRUE
2              NA                   0                 0                TRUE
3              NA                   0                 0                TRUE
4              NA                   0                 0                TRUE
5               1                   0                 0                TRUE
6              NA                   1                 0                TRUE
7              NA                   1                 1                TRUE
8              NA                   1                 0                TRUE
9               1                   0                 0                TRUE
10             NA                   0                 0                TRUE
   
   is_table_reservation_supported has_table_booking
1                               1                 0
2                               0                 0
3                               0                 0
4                               0                 0
5                               1                 0
6                               0                 0
7                               0                 0
8                               0                 0
9                               1                 0
10                              0                 0
                              
                              phone_numbers establishment R.has_menu_status.delivery
1                              011 66992235           Bar                         -1
2                            +91 8448444960 Casual Dining                         -1
3                011 26110787, 011 26110788          Café                         -1
4                011 46215152, 011 66325124   Fine Dining                         -1
5                            +91 8061756000 Casual Dining                         -1
6                011 47685301, 011 47685304    Sweet Shop                         -1
7  0124 4271101, 0124 4271102, 0124 4271103   Quick Bites                          1
8                              011 41403240   Quick Bites                         -1
9                            +91 8061756000 Casual Dining                         -1
10             +91 9871117968, 011 66175151   Fine Dining                         -1
   
   R.has_menu_status.takeaway
1                          -1
2                          -1
3                          -1
4                          -1
5                          -1
6                          -1
7                          -1
8                          -1
9                          -1
10                         -1
                                 
                                                                                   address
1                                        8, World Mark 2, IGI Airport, Aerocity, New Delhi
2                                                       Gardens Galleria, Sector 38, Noida
3                10, Santushti Shopping Complex, Race Course Road, Chanakyapuri, New Delhi
4                                                      ITC Maurya, Chanakyapuri, New Delhi
5         2nd Floor, Munshilal Building, Block N, Outer Circle, Connaught Place, New Delhi
6                                         M-48, 48/2, and 48/3, Connaught Place, New Delhi
7                                                  SCO 17, Main Market, Sector 31, Gurgaon
8                                        2nd Floor, Select Citywalk Mall, Saket, New Delhi
9  A-79 A, Ground Floor, Hotel Savoy Suites, Captain Vijyant Thapar Marg, Sector 16, Noida
10                                                        The Lodhi, Lodhi Road, New Delhi
                      
                      locality      city city_id      latitude     longitude zipcode
1                     Aerocity New Delhi       1 28.5515370000 77.1227040000        
2                    Sector 38     Noida       1 28.5637110510 77.3229883611        
3                 Chanakyapuri New Delhi       1 28.5951426153 77.1979655698        
4     ITC Maurya, Chanakyapuri New Delhi       1 28.5982159011 77.1736473218       0
5              Connaught Place New Delhi       1 28.6303528452 77.2207485884        
6              Connaught Place New Delhi       1 28.6341154631 77.2222033516       0
7                    Sector 31   Gurgaon       1 28.4529982115 77.0504662022       0
8  Select Citywalk Mall, Saket New Delhi       1 28.5292057837 77.2193729505        
9                    Sector 16     Noida       1 28.5802547475 77.3151626810        
10       The Lodhi, Lodhi Road New Delhi       1 28.5920639406 77.2376998141       0
   
   country_id                       locality_verbose aggregate_rating rating_text
1           1                    Aerocity, New Delhi              4.4   Very Good
2           1                       Sector 38, Noida              3.7        Good
3           1                Chanakyapuri, New Delhi              4.3   Very Good
4           1    ITC Maurya, Chanakyapuri, New Delhi              4.6   Excellent
5           1             Connaught Place, New Delhi              4.2   Very Good
6           1             Connaught Place, New Delhi              4.1   Very Good
7           1                     Sector 31, Gurgaon              4.1   Very Good
8           1 Select Citywalk Mall, Saket, New Delhi              4.0   Very Good
9           1                       Sector 16, Noida              4.2   Very Good
10          1       The Lodhi, Lodhi Road, New Delhi              4.9   Excellent
   
   rating_color votes rating_obj.title.text rating_obj.bg_color.type
1        5BA829   455                   4.4                     lime
2        9ACD32    83                   3.7                     lime
3        5BA829  3215                   4.3                     lime
4        3F7E00  4486                   4.6                     lime
5        5BA829  4863                   4.2                     lime
6        5BA829  2224                   4.1                     lime
7        5BA829  2245                   4.1                     lime
8        5BA829  3304                   4.0                     lime
9        5BA829  2963                   4.2                     lime
10       3F7E00  3678                   4.9                     lime
   
   rating_obj.bg_color.tint all_reviews.reviews
1                       700                NULL
2                       600                NULL
3                       700                NULL
4                       800                NULL
5                       700                NULL
6                       700                NULL
7                       700                NULL
8                       600                NULL
9                       700                NULL
10                      800                NULL

```
```{r}
get_locations(key=key,query="van",count=1)
```

```
  entity_type     entity_id                title    latitude    longitude    city_id      city_name    country_id     country_name
         city          9560   Van Alstyne, Texas    33.42251    -96.57942       9560    Van Alstyne           216    United States
```

```{r}
get_dailymenu(key=key, res_id="16507624")
```

```
  daily_menu.daily_menu_id daily_menu.start_date         daily_menu.name
1                 17178053   2020-02-04 00:00:00                 Polévky
2                 17178059   2020-02-04 00:00:00 Předkrmy / Jídla k pivu
3                 17178061   2020-02-04 00:00:00            Hlavní chody
4                 17178064   2020-02-04 00:00:00                  Saláty
5                 17191110   2020-02-04 00:00:00                  Dezert
                                                                                 
                                                                                                                                                      daily_menu.dishes
1 634207002, Bramboračka s hříbky, 45 Kč
2 634206981, 634206982, 634206983, 634206984, 634206985, 634206986, 634206987, 634206988, 634206989, 634206990, Kachní paštika s brusinkami, mandlemi a cibulovou marmeládou, Studený roastbeef s hořčičnou omáčkou a okurkou, Rillettes z vepřového masa s hořčičnou omáčkou, Nakládaný hermelín, Nakládané olomoucké tvarůžky  , Domácí škvarková pomazánka s cibulkou, Tlačenka s cibulkou a octem, Jehněčí klobásky s hořčičným dipem a malým zelným salátem, Špekáčky na černém pivu, Slané pražené mandle (80 g), 89 Kč, 99 Kč, 85 Kč, 85 Kč, 79 Kč, 65 Kč, 59 Kč, 89 Kč, 89 Kč, 79 Kč
3 634206991, 634206992, 634206993, 634206994, 634206995, 634206996, 634206997, 634206998, Dančí svíčková s karlovarským knedlíkem a brusinkami, Grilovaný flapsteak s gratinovanými bramborami a zelenými fazolkami, omáčka z pečeného česneku, Marinovaná pečená vepřová žebra s česnekovou majonézou, Medailonky z vepřové panenky s pečenou paprikou, brambory Grenaille a omáčka s rozmarýnem, Rolované farmářské kuře marinované v brandy, smetanová br. kaše s list. špenátem, Bůček na černém pivu s červeným zelím a bramborovými špalíky, Smažený řízek z přeštického prasátka s lehkým bramborovým salátem, Naše bramborové špalíky se smetanovým listovým špenátem, 239 Kč, 249 Kč, 196 Kč, 229 Kč, 165 Kč, 149 Kč, 185 Kč, 99 Kč
4 635121494, 635121495, 635121496, Salát se smaženými kuřecími proužky, Salát s roastbeefem a pikantním česnekovým dresinkem, Salát z mladého špenátu a hrášku s šalotkou a čerstvým kozím sýrem, 129 Kč, 149 Kč, 129 Kč
5 631103520, 631103521, Čokoládová pěna s višněmi marinovanými v griotce, Šlehaná zakysaná smetana s medem a čerstvým ovocem, máta, 55 Kč, 55 Kč

```
```{r}
get_restaurant(key=key, res_id="16774318")
```
```
  R.has_menu_status.delivery        R.has_menu_status.takeaway            R.res_id
                          -1                                -1            16774318
  
  apikey                  id                              name
     key            16774318             Otto Enoteca Pizzeria
                                                                                                                                      url
  https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
   
                                                  address                 locality             city
  One Fifth Avenue at 8th Street, Greenwich Village 10003        Greenwich Village    New York City
  
  city_id            latitude            longitude    zipcode     country_id       locality_verbose
      280       40.7318200000       -73.9965400000      10003            216      Greenwich Village
  
  switch_to_order_menu         cuisines
                     0   Pizza, Italian
                                                                                 timings
  12 Noon to 11 PM (Mon-Thu), 11:30 AM to 12 Midnight (Fri-Sat), 11:30 AM to 11 PM (Sun)
  
  average_cost_for_two price_range currency    highlights1 highlights2 highlights3
                    40           3        $ Serves Alcohol    Delivery       Lunch
  
  highlights4        highlights5    highlights6         highlights7    highlights8
       Dinner Takeaway Available    Credit Card Vegetarian Friendly        Fullbar
                
                highlights9      highlights10   opentable_support   is_zomato_book_res
  Table booking recommended    Indoor Seating                   0                    0
  
  mezzo_provider is_book_form_web_view book_form_web_view_url book_again_url
           OTHER                     0                                      
                                                                                                                                 thumb
  https://b.zmtcdn.com/data/pictures/8/16774318/b16e382e9f6696f911b600b7e5ca6839.jpg?fit=around%7C200%3A200&crop=200%3A200%3B%2A%2C%2A
  
  aggregate_rating   rating_text   rating_color   rating_obj.text   rating_obj.bg_color.type
               4.4     Very Good         5BA829               4.4                       lime
  
  rating_obj.bg_color.tint   votes   all_reviews_count
                       700     568                  97
                                                                                                                                             photos_url
  https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
  
  photo_count    photos.photo.id
           88   u_A1MTE1MTYxNDYz
                                                                                                                                photos.photo.url
  https://b.zmtcdn.com/data/reviews_photos/ef8/d451664187858a70dd79bd8750e0fef8_1442095040.JPG?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A
                                                                                                                                                                                                                                                                                                                          photos.photo.thumb_url
  https://b.zmtcdn.com/data/reviews_photos/ef8/d451664187858a70dd79bd8750e0fef8_1442095040.JPG?impolicy=newcropandfit&cropw=900&croph=900&cropoffsetx=112&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore
  
  photos.photo.res_id   photos.photo.caption   photos.photo.timestamp   photos.photo.friendly_time
             16774318                                      1442095369                 Sep 13, 2015
  
  photos.photo.width    photos.photo.height    photos.photo.user.name
                 640                    640             Feisty Foodie
  
  photos.photo.user.zomato_handle      photos.photo.user.foodie_level
                     feistyfoodie                         Connoisseur
  
  photos.photo.user.foodie_level_num   photos.photo.user.foodie_color
                                  13                           e95151
                                                                   
                                                                   photos.photo.user.profile_url
  https://www.zomato.com/feistyfoodie?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
                                                                                                             
                                                                                                             photos.photo.user.profile_image
  https://b.zmtcdn.com/data/user_profile_pictures/7d3/8268699d29fcede843861dd0c07b27d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A
  
  photos.photo.user.profile_deeplink
                 zomato://u/20641164
                                                                                                                                                                                                                                                                                                                                        menu_url
  https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
                                                                      featured_image
  https://b.zmtcdn.com/data/pictures/8/16774318/b16e382e9f6696f911b600b7e5ca6839.jpg
  
  has_online_delivery   is_delivering_now   include_bogo_offers                     deeplink
                    0                   0                  TRUE zomato://restaurant/16774318
  
  is_table_reservation_supported   has_table_booking
                               0                   0
       
                                                                                                                                             events_url
  https://www.zomato.com/new-york-city/otto-enoteca-pizzeria-greenwich-village/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
                   
                   phone_numbers   review    establishment
  (212) 995-9559, (212) 995-9559     NULL         Pizzeria
  
```

```{r}
get_reviews(key=key, res_id="16774318")
```

```
  review.rating
1           5.0
2           4.0
3           4.0
4           3.0
5           3.5
 review.review_text
1                                                  
2
3
4 Good restaurant pocket friendly menu great sitting arrangements and beautiful ambience. Has gobi manchurian spring roll and chilli chicken my favourite kiwi shake. I enjoyed a lot
5 The pizza was decent, not the best I've had. The staff was great- knowledgeable and willing to give recommendations. Extensive wine list. The star of the meal, though was the "weekly" fromaggio which was burrata with spring vegetables. Impeccable flavours (and enough to act as a meal if you so desire- in fact, I thought it would have been great served on crust as a pizza). Enjoyable dining experience overall.
  
  review.id review.rating_color review.review_time_friendly review.rating_text
1  45706756              305D02                3 months ago            Insane!
2  45689448              5BA829                3 months ago             Great!
3  45685699              5BA829                3 months ago             Great!
4  43278019              CDD614                8 months ago            Average
5  30119358              9ACD32                Apr 22, 2017        Good Enough
  
  review.timestamp review.likes review.comments_count review.user.name
1       1571476136            0                     0 Siddharth Sharma
2       1571391100            0                     0 Jennifer Kinleiy
3       1571375261            0                     0     Rahul Prasad
4       1559125150            0                     0      Wild Foodie
5       1492821318            0                     0             Jess
  
  review.user.foodie_level review.user.foodie_level_num review.user.foodie_color
1             Super Foodie                            9                   f58552
2             Super Foodie                           10                   f58552
3             Super Foodie                            9                   f58552
4                     <NA>                           NA                   e95151
5                   Foodie                            3                   ffd35d
                                                                                         
                                                                                             review.user.profile_url
1 https://www.zomato.com/users/siddharth-sharma-144912900?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
2 https://www.zomato.com/users/jennifer-kinleiy-144763426?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
3     https://www.zomato.com/users/rahul-prasad-144721676?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
4      https://www.zomato.com/users/wild-foodie-115723433?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
5              https://www.zomato.com/users/jess-30953380?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
                                                                                          
                                                                                                                   review.user.profile_image
1                                      https://b.zmtcdn.com/images/user_avatars/mug_2x.png?fit=around%7C200%3A200&crop=200%3A200%3B%2A%2C%2A
2 https://b.zmtcdn.com/data/user_profile_pictures/484/cee2d5f7654008df694851492f668484.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A
3 https://b.zmtcdn.com/data/user_profile_pictures/658/e37826b8b9cde967f2a10f78f9366658.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A
4                                     https://b.zmtcdn.com/images/user_avatars/cupcake.png?fit=around%7C200%3A200&crop=200%3A200%3B%2A%2C%2A
5                                      https://b.zmtcdn.com/images/user_avatars/mug_2x.png?fit=around%7C200%3A200&crop=200%3A200%3B%2A%2C%2A
  
  review.user.profile_deeplink
1         zomato://u/144912900
2         zomato://u/144763426
3         zomato://u/144721676
4         zomato://u/115723433
5          zomato://u/30953380

```

```{r}
get_search(key=key, q="van")
```

```
 restaurant.apikey   restaurant.id    restaurant.name
               key        16647276    The Vanilla Pod
               
                                                                                                            restaurant.url
  https://www.zomato.com/penticton-bc/the-vanilla-pod-penticton?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
  
  restaurant.switch_to_order_menu               restaurant.cuisines                         restaurant.timings 
                                0          Pacific Northwest, Pizza    Closed (Mon),11:30 AM to 9 PM (Tue-Sun) 
                    
  restaurant.average_cost_for_two            restaurant.price_range                        restaurant.currency 
                               40                                 3                                          $
                               
                                                                                                                          restaurant.highlights
  Lunch, Dinner, Outdoor Seating, Private Dining Area Available, Gluten Free Options, Table booking recommended, Kid Friendly, Wifi, Ocean Wise
  
                restaurant.offers       restaurant.opentable_support              restaurant.is_zomato_book_res
                             NULL                                  0                                          0
 
        restaurant.mezzo_provider   restaurant.is_book_form_web_view          restaurant.book_form_web_view_url       restaurant.book_again_url
                            OTHER                                  0             
   
  restaurant.thumb
  https://b.zmtcdn.com/data/reviews_photos/368/ee267e41f36eccf81c96e8efe1480368_1497902196.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=58&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore
  
  restaurant.all_reviews_count
                            13
  
  restaurant.photos_url
  https://www.zomato.com/penticton-bc/the-vanilla-pod-penticton/photos?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1#tabtop
  
  restaurant.photo_count
                       8
 
 restaurant.photos
  u_0NDEyMDkwODMwM 
  u_2MDkzNjI1MTE5M
  u_g4NTk3MjY5NTk2
  u_I3MDY2Mzg4ODY4
  u_YzMDM2NzgyMTY5
  u_MjQzMDQ3NTI3NT
  u_zkzNTIxNTMzMTE
  u_E4NDI3MjAwMzgx
  
https://b.zmtcdn.com/data/reviews_photos/368/ee267e41f36eccf81c96e8efe1480368_1497902196.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A    https://b.zmtcdn.com/data/reviews_photos/457/584003825d5b4725f62f8bdd1150a457_1505608477.jpg, https://b.zmtcdn.com/data/reviews_photos/35f/8b92a7d46625a31375dad3a6daf4935f_1497902214.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A, https://b.zmtcdn.com/data/reviews_photos/e3d/a14c30ae979f01acea842e97fbfd0e3d_1497902240.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A, https://b.zmtcdn.com/data/reviews_photos/c97/f15450b2072a768c4f9c6345e0522c97_1497902223.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A,     https://b.zmtcdn.com/data/reviews_photos/9dd/3800cc7629d6709ffa2e72fcdf1289dd_1497902190.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A, https://b.zmtcdn.com/data/reviews_photos/50a/99e5d39187d209bd3cf9e4239158a50a_1497902253.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A, https://b.zmtcdn.com/data/reviews_photos/f0e/1a8a37f6e3185ca9694bca9c86e12f0e_1497902231.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A, https://b.zmtcdn.com/data/reviews_photos/368/ee267e41f36eccf81c96e8efe1480368_1497902196.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=58&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, https://b.zmtcdn.com/data/reviews_photos/457/584003825d5b4725f62f8bdd1150a457_1505608477.jpg?impolicy=newcropandfit&cropw=2448&croph=2448&cropoffsetx=0&cropoffsety=508&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, https://b.zmtcdn.com/data/reviews_photos/35f/8b92a7d46625a31375dad3a6daf4935f_1497902214.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=190&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, https://b.zmtcdn.com/data/reviews_photos/e3d/a14c30ae979f01acea842e97fbfd0e3d_1497902240.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=244&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, https://b.zmtcdn.com/data/reviews_photos/c97/f15450b2072a768c4f9c6345e0522c97_1497902223.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=280&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, https://b.zmtcdn.com/data/reviews_photos/9dd/3800cc7629d6709ffa2e72fcdf1289dd_1497902190.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=269&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, https://b.zmtcdn.com/data/reviews_photos/50a/99e5d39187d209bd3cf9e4239158a50a_1497902253.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=335&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, https://b.zmtcdn.com/data/reviews_photos/f0e/1a8a37f6e3185ca9694bca9c86e12f0e_1497902231.jpg?impolicy=newcropandfit&cropw=800&croph=800&cropoffsetx=273&cropoffsety=0&cropgravity=NorthWest&fitw=200&fith=200&fittype=ignore, 
  
  16647276     1497902288     Jun 20, 2017      640      640
  16647276     1505608478     Sep 17, 2017     2448     3264
  16647276     1497902288     Jun 20, 2017      640      640
  16647276     1497902288     Jun 20, 2017      640      640
  16647276     1497902288     Jun 20, 2017      640      640
  16647276     1497902288     Jun 20, 2017      640      640
  16647276     1497902288     Jun 20, 2017      640      640
  16647276     1497902288     Jun 20, 2017      640      640
  
  Prince Gastronome   Super Foodie  11   f58552
           KMcClurg         Foodie   3   ffd35d
  Prince Gastronome   Super Foodie  11   f58552
  Prince Gastronome   Super Foodie  11   f58552
  Prince Gastronome   Super Foodie  11   f58552
  Prince Gastronome   Super Foodie  11   f58552
  Prince Gastronome   Super Foodie  11   f58552
  Prince Gastronome   Super Foodie  11   f58552

https://www.zomato.com/users/prince-gastronome-22649291?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1,   https://www.zomato.com/users/kmcclurg-30161476?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1, https://www.zomato.com/users/prince-gastronome-22649291?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1, https://www.zomato.com/users/prince-gastronome-22649291?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1, https://www.zomato.com/users/prince-gastronome-22649291?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1, https://www.zomato.com/users/prince-gastronome-22649291?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1, https://www.zomato.com/users/prince-gastronome-22649291?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1, https://www.zomato.com/users/prince-gastronome-22649291?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1, https://b.zmtcdn.com/data/user_profile_pictures/4d3/429e28f555a63f3a801aa5f7d9dfb4d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A, https://b.zmtcdn.com/images/user_avatars/mug_2x.png?fit=around%7C200%3A200&crop=200%3A200%3B%2A%2C%2A, https://b.zmtcdn.com/data/user_profile_pictures/4d3/429e28f555a63f3a801aa5f7d9dfb4d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A, https://b.zmtcdn.com/data/user_profile_pictures/4d3/429e28f555a63f3a801aa5f7d9dfb4d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A, https://b.zmtcdn.com/data/user_profile_pictures/4d3/429e28f555a63f3a801aa5f7d9dfb4d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A, https://b.zmtcdn.com/data/user_profile_pictures/4d3/429e28f555a63f3a801aa5f7d9dfb4d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A, https://b.zmtcdn.com/data/user_profile_pictures/4d3/429e28f555a63f3a801aa5f7d9dfb4d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A, https://b.zmtcdn.com/data/user_profile_pictures/4d3/429e28f555a63f3a801aa5f7d9dfb4d3.jpg?fit=around%7C100%3A100&crop=100%3A100%3B%2A%2C%2A, 

zomato://u/22649291, 
zomato://u/30161476, 
zomato://u/22649291, 
zomato://u/22649291, 
zomato://u/22649291, 
zomato://u/22649291, 
zomato://u/22649291, 
zomato://u/22649291, 

NA, 
NA, 
NA, 
NA, 
NA, 
  , 
NA, 
NA
  
  restaurant.menu_url
  https://www.zomato.com/penticton-bc/the-vanilla-pod-penticton/menu?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1&openSwipeBox=menu&showMinimal=1#tabtop
  
  restaurant.featured_image
  https://b.zmtcdn.com/data/reviews_photos/368/ee267e41f36eccf81c96e8efe1480368_1497902196.jpg?fit=around%7C640%3A640&crop=640%3A640%3B%2A%2C%2A
  
  restaurant.has_online_delivery
                               0
  
    restaurant.is_delivering_now
                               0                          
  
  restaurant.include_bogo_offers
                            TRUE
  
            restaurant.deeplink 
   zomato://restaurant/16647276

restaurant.is_table_reservation_supported
                                        0
  
   restaurant.has_table_booking
                              0
  
  restaurant.events_url
  https://www.zomato.com/penticton-bc/the-vanilla-pod-penticton/events#tabtop?utm_source=api_basic_user&utm_medium=api&utm_campaign=v2.1
  
  restaurant.phone_numbers 
         +1 (250) 493-9463            
  
  restaurant.establishment
                      NULL
  
  restaurant.establishment_types
                            NULL
  
  restaurant.R.res_id 
            16647276          
  
  restaurant.R.has_menu_status.delivery
                                     -1
  
  restaurant.R.has_menu_status.takeaway
                                     -1 
  
            restaurant.location.address
  425 Middle Bench Rd, Penticton V2A8S5
  
            restaurant.location.locality  
                               Penticton    
  
                restaurant.location.city
                               Penticton
  
             restaurant.location.city_id
                                    2996
  
            restaurant.location.latitude 
                           49.5133854000               
  
           restaurant.location.longitude
                         -119.5714503000   
  
             restaurant.location.zipcode
                                  V2A8S5
  
          restaurant.location.country_id 
                                      37        
  
    restaurant.location.locality_verbose
                    Penticton, Penticton
  
 restaurant.user_rating.aggregate_rating 
                                     3.5                            
  
      restaurant.user_rating.rating_text
                                    Good
 
     restaurant.user_rating.rating_color 
                                  9ACD32 
  
            restaurant.user_rating.votes
                                      30
  
     restaurant.user_rating.rating_obj.title.text
                                              3.5
 
  restaurant.user_rating.rating_obj.bg_color.type
                                             lime
  
  restaurant.user_rating.rating_obj.bg_color.tint
                                          
  
          restaurant.all_reviews.reviews
                                    NULL
                                    
```











